Integration of Multiple Constraints in ACG

### 2013-07-24 lenls/abstract.tex
LENLS: Final proof-read of the abstract

In this paper we focus on the problem of constructing a wide-coverage ACG. We
identify a problem that comes up when one tries to enforce multiple
constraints/dependencies in a single ACG and we propose a generalization of
the formalism which resolves to the issue.

@@

When describing languages, we are usually interested in systems of more
than one ACG and diagrams such as the ones on Figure~\ref{fig:acg-comp}
have been used to explain them.

@@

In French, negation is signalled by prepending the particle \emph{ne} to
the negated verb in conjunction with using a properly placed
accompanying word, such as a negative determiner in one of the verb's
arguments. This phenomenon has been elegantly formalized in the Frigram
interaction grammar \cite{perrier2007french}.

@@

The two paradigms under which we can interpret ACGs are equivalent in
the context of plain ACGs whose diagrams are arborescent and the two
metaphors (nodes as languages and nodes as terms) can be used
interchangeably. We back this up formally by showing that for every node
$u$ in every arborescent G-ACG $\mathcal{G}$, we have
$\mathcal{E}_{\mathcal{G}}(u) = \mathcal{P}_{\mathcal{G}}(u)$. However,
as we start to consider non-arborescent graphs, we find, interestingly,
that the two paradigms diverge (i.e. $\exists \mathcal{G},
u.\ \mathcal{E}_{\mathcal{G}}(u) \neq \mathcal{P}_{\mathcal{G}}(u)$).

@@

In the end, this lets us define the syntax in a clean way using the
idiomatic style of categorial grammars (simple atomic types like $N$,
$NP$ and $S$) and then define the constraints themselves the same way as
they are defined in papers which try to formalize them individually
(such as the case with \cite{pogodalla2012controlling}).

>>>>

In this paper, we focus on the problem of constructing a wide-coverage ACG. We
identify a problem that comes up when one tries to enforce multiple
constraints/dependencies in a single ACG and we propose a generalization of
the formalism which resolves the issue.

@@

When describing languages, we are usually interested in systems of more than
one ACG, and diagrams such as the ones on Figure~\ref{fig:acg-comp} have been
used to explain them.

@@

In French, negation is signalled by prepending the particle \emph{ne} to the
negated verb in conjunction with using a properly placed accompanying word,
such as a negative determiner, in one of the verb's arguments. This phenomenon
has been elegantly formalized in the Frigram interaction grammar
\cite{perrier2007french}.

@@

The two paradigms under which we can interpret ACGs are equivalent in the
context of plain ACGs whose diagrams are arborescent and hence the two
metaphors (nodes as languages and nodes as terms) can be used
interchangeably. We back this up formally by showing that for every node $u$
in every arborescent G-ACG $\mathcal{G}$, we have
$\mathcal{E}_{\mathcal{G}}(u) = \mathcal{P}_{\mathcal{G}}(u)$. However, as we
start to consider non-arborescent graphs, we find, interestingly, that the two
paradigms diverge (i.e. $\exists \mathcal{G}, u.\ \mathcal{E}_{\mathcal{G}}(u)
\neq \mathcal{P}_{\mathcal{G}}(u)$).

@@

In the end, this lets us define the syntax in a clean way using the idiomatic
style of categorial grammars (simple atomic types like $N$, $NP$ and $S$) and
then define the constraints themselves the same way as they are defined in
papers which try to formalize them individually (such as is the case with
\cite{pogodalla2012controlling}).
